\documentclass[a4paper, 11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usepackage{moreverb}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{listings} 
\usepackage{lastpage}
\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}
\usepackage{color}
\usepackage{xcolor}
\usepackage{epstopdf} 
%font change
\renewcommand{\familydefault}{\sfdefault}

\newcommand{\HRule}{\rule{\linewidth}{0.3mm}}
\newcommand{\nl}{\\[0.1cm]}
\newcommand{\s}{\vspace{0.3cm}}
\newcommand{\emptypage}{\newpage \thispagestyle{empty} \mbox{}\newpage}
\newcommand{\smore}{\vspace{0.6cm}}
\newcommand{\emphasis}[1]{\textbf{#1}}

\usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}

\lstset{frame=single,basicstyle=\ttfamily}

\lstdefinelanguage{popc}{%
   morekeywords={%
   %od
      od, url, power, @, 100, 80, machine, POPString, search
  },
  sensitive=true,
  morestring=[b]',
}

\addto\captionsenglish{%
  \renewcommand{\listfigurename}{}%
	\renewcommand\refname{}
}



%Header and footer 
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}

%Header definition
\renewcommand{\headrulewidth}{0.5pt}
\lhead{POP-Java : User and Installation Manual}
\rhead{Bachelor Thesis 2010}

%Footer definition
\renewcommand{\footrulewidth}{0.5pt}
\cfoot{\today}
\lfoot{Clément Valentin, Beat Wolf}
\rfoot{Page \thepage ~on \pageref{LastPage}}

%remove indent for paragraph
\parindent0ex 

%\setlength{\parskip2ex}







\begin{document}

% TITLE
\input{title.tex}

%\emptypage
% CONTENTS
\tableofcontents
\pagebreak

\section{Remark on this document}
This document is part of the bachelor thesis project named "POP-Java". For more technical informations about POP-Java, please see the document "POP-Java - Technical Report"\cite{popjava_tech}. The two next chapters ("Introduction and Background" and "Parallel Object Model") are very inspiring of the same chapters of the "Parallel Object Programming C++ - User and Installation Manual"\cite{popc_intro}. Notice that some figures and some texts have been taken from the same document.

% INTRODUCTION
%\emptypage
\pagebreak
\section{Introduction and background}
\input{intro.tex}

% POP
\pagebreak
\section{Parallel Object Model}
\input{popmodel.tex}

% POP-JAVA Dev
%\emptypage
\pagebreak
\section{Developing POP-Java application}
\input{development.tex}

% COMPILE AND RUN
\pagebreak
\section{Compile and run a POP-Java application}
\input{compile.tex}

% POP-Java POP-C++
%\emptypage
\pagebreak
\section{Developing POP-Java and POP-C++ mixed application}
\input{mixed.tex}

% POP-Java plugin
\pagebreak
\section{POP-Java plugin}
\input{plugin.tex}

% INSTALLATION
\pagebreak
\section{Installation}
\input{install.tex}

%DOCUMENTATION AND EXAMPLE
%\emptypage
\pagebreak
\section{Documentation and examples}
\input{doc_ex.tex}

% TROURBLESHOOTING
%\emptypage
\pagebreak
\section{Troubleshooting}
\input{troubleshooting.tex}

%\emptypage
\pagebreak
\section{Table of figures}
\listoffigures{}


%\emptypage
\pagebreak
\section{References}
\begin{thebibliography}{9}

\bibitem{popjava_tech}
	Clément Valentin,
  	\emph{POP-Java - Technical Report}.
	EIA-FR, Fribourg, Switzerland,
	August 2010.

\bibitem{popc_intro}
	The POP-C++ Team,
  	\emph{Parallel Object Programming C++, User and installation Manual}.
	Grid and Ubiquitous Computing Group, EIA-FR, Fribourg, Switzerland,
	2010.

\bibitem{popc_thesis}
	Dr. Thuan-Anh Nguyen,
  	\emph{An object-oriented model for adaptive high performance computing on the computational GRID}.
	EPFL, Lausanne, Switzerland,
	2005.

\bibitem{Allcock02}
W.~Allcock, J.~Bester, J.~Bresnahan, A.~Chervenak, L.~Liming, S.~Meder, and
  S.~Tuecke.
\newblock {\em GridFTP Protocol Specification}.
\newblock GGF GridFTP Working Group Document, September 2002.
\newblock http://www.globus.org/research/papers.htm.

\bibitem{Czajkowski98}
K.~Czajkowski, I.~Foster, N.~Karonis, C.~Kesselman, S.~Martin, W.~Smith, and
  S.~Tuecke.
\newblock A resource management architecture for metacomputing systems.
\newblock In {\em Proc. IPPS/SPDP '98 Workshop on Job Scheduling Strategies for
  Parallel Processing}, pages 62--82, 1998.

\bibitem{Foster98:2}
I.~Foster and N.~Karonis.
\newblock A grid-enabled mpi: Message passing in heterogeneous distributed
  computing systems.
\newblock In {\em Proc. 1998 SC Conference}, November 1998.

\bibitem{Foster97}
I.~Foster and C.~Kesselman.
\newblock Globus: A metacomputing infrastructure toolkit.
\newblock {\em Intl J. Supercomputer Applications}, 11(2):115--128, 1997.

\bibitem{Foster02}
I.~Foster, C.~Kesselman, J.~Nick, and S.~Tuecke.
\newblock Grid services for distributed system integration.
\newblock {\em Computer}, 35(6), 2002.

\bibitem{Grimshaw99}
Andrew Grimshaw, Adam Ferrari, Fritz Knabe, and Marty Humphrey.
\newblock Legion: An operating system for wide-area computing.
\newblock {\em IEEE Computer}, 32:5:29--37, May 1999.

\bibitem{Karonis03}
N.~Karonis, B.~Toonen, and I.~Foster.
\newblock {MPICH-G2}: A grid-enabled implementation of the message passing
  interface.
\newblock {\em Journal of Parallel and Distributed Computing}, 2003.

\bibitem{Nguyen07}
Kuonen~P. Nguyen, T.~A.
\newblock Programming the grid with pop-c++.
\newblock {\em Future Generation Computer Systems (FGCS)}, 23(1):23--30,
  January 2007.

\bibitem{Nguyen04}
Tuan-Anh Nguyen.
\newblock {\em An Object-oriented model for adaptive high performance computing
  on the computational Grid}.
\newblock PhD thesis, Swiss Federal Institute of Technology-Lausanne, 2004.

\bibitem{corba26}
{Object Management Group}, Framingham, Massachusetts.
\newblock {\em The Common Object Request Broker: Architecture and Specification
  --- Version 2.6}, December 2001.

\bibitem{Roy00}
A.~Roy, I.~Foster, W.~Gropp, N.~Karonis, V.~Sander, and B.~Toonen.
\newblock \mbox{MPICH-GQ}: Quality-of-service for message passing programs.
\newblock In {\em Proc. of the IEEE/ACM SC2000 Conference}, November 2000.

\bibitem{Stockinger01}
H.~Stockinger, A.~Samar, B.~Allcock, I.~Foster, K.~Holtman, and B.~Tierney.
\newblock File and object replication in data grids.
\newblock In {\em 10th IEEE Symposium on High Performance and Distributed
  Computing (HPDC2001)}, 2001.
\newblock San Francisco, California.

\bibitem{Tong03}
Weiqin Tong, Jingbo Ding, and Lizhi Cai.
\newblock A parallel programming environment on grid.
\newblock In {\em International Conference on Computational Science 2003},
  pages 225--234, 2003.

\bibitem{Welch03}
V.~Welch, F.~Siebenlist, I.~Foster, J.~Bresnahan, K.~Czajkowski, J.~Gawor,
  C.~Kesselman, S.~Meder, L.~Pearlman, and S.~Tuecke.
\newblock Security for grid services.
\newblock In IEEE Press, editor, {\em Twelfth International Symposium on High
  Performance Distributed Computing (HPDC-12)}, 2003.

\bibitem{Williams00}
Tiffani~L. Williams and Rebecca~J. Parsons.
\newblock The heterogeneous bulk synchronous parallel model.
\newblock {\em Lecture Notes in Computer Science}, 1800, 2000.

\end{thebibliography}

\pagebreak
\appendix
\input{appendix.tex}


\end{document}
